The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-02-10 article/article.tex
add asymptotic bounds for L
analysis of always go left

\begin{align}
F_d(k) = \sum_{i=1}^{d}F_d(k-i)
\end{align}
Furthermore, define 
\begin{align}
\Phi_d = \lim_{k \rightarrow \infty} \sqrt[k]{F_d(k)}
\end{align}
Notice that $F_2$ corresponds to the usual Fibonacci numbers, while $\Phi_2 $ corresponds to the golden ratio \cite{Knuth73}, which is generalized to $\Phi_d$, for which 
\begin{align}
i, j \in \mathbb{N}, i < j \Rightarrow \Phi_i < \Phi_j
\end{align}
and 
\begin{align}
\lim_{d\rightarrow \infty} \Phi_d = 2
\end{align}
hold.

@@

For any constant $\alpha > 0 $, let
\begin{align}
L \geq \log_d\log_2 n + \log_d\left(1+\alpha\right)
\end{align}
and $n$ be large enough such that 
\begin{align}
L \in \Theta \left(\ln \ln n \right)
\end{align}
Then, 
\begin{align}
p_{swt} &\leq n \cdot 2^{{-d}^{\log_d\log_2 n + \log_d\left(1+\alpha\right)}} \\
		&= n \cdot 2^{-{d}^{\log_d\log_2 n}\cdot d^{\log_d \cdot\left(1+\alpha\right)}} \\
		&= n \cdot \left( 2^{-\log_2 n \cdot \left(1+ \alpha \right)} \right) \\
		&= n \cdot n^{-\left(1+\alpha\right)} \\
		&= n^{-\alpha}
\end{align}

\todo{add the asymptotic bound}

@@

A $d$-ary asymmetric witness tree of order $L$ has the structure of the Fibonacci tree $T_d(d \cdot L+1)$ and thus has $F_d(d\cdot L + 1) \geq \Phi_d^{d\cdot L-1}$ \todo{How to get this inequality?} leaves.

@@

The above results imply the same probability for the activation of an asymmetric witness tree as we derived in Section \ref{sec:analysis:probabilitySymWT} for the activation of a symmetric witness tree, that is
\begin{align}
p_{awt} &\leq n 2^{-l}
\end{align}
However, the number of leaves is larger, since 
\begin{align}
l \geq \Phi_d^{d\cdot L -1}
\end{align}
holds\footnote{see Section \ref{sec:analysis:definitionAsymWT} for details}.

For any constant $\alpha > 0$, let 
\begin{align}
L = \left\lceil{\frac{\ln\log_2 n + \ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d}}\right  \rceil +1
\end{align}
and $n$ be large enough such that
\begin{align}
L \in \Theta\left(\frac{\ln\ln n}{d\cdot \ln \Phi_d}\right)
\end{align}

>>>>

\begin{align}
F_d(k) = \sum_{i=1}^{d}F_d(k-i)
\end{align}
Furthermore, define 
\begin{align}\label{eqn:goldenFib}
\Phi_d = \lim_{k \rightarrow \infty} \sqrt[k]{F_d(k)}
\end{align}
Notice that $F_2$ corresponds to the usual Fibonacci numbers, while $\Phi_2 $ corresponds to the golden ratio \cite{Knuth73}, which is generalized to $\Phi_d$, for which 
\begin{align}
i, j \in \mathbb{N}, i < j \Rightarrow \Phi_i < \Phi_j
\end{align}
and 
\begin{align}
\lim_{d\rightarrow \infty} \Phi_d = 2
\end{align}
hold.

@@

For any constant $\alpha > 0 $, let
\begin{align}
L &\geq \log_d\log_2 n + \log_d\left(1+\alpha\right)
\end{align}
and note that
\begin{align}
L &\geq  \frac{\ln\log_2 n}{\ln d} + \frac{\ln(1+\alpha)}{\ln d} \\
   &= \frac{\ln \log_2 n}{\ln d} \cdot \left(1 + \frac{\ln\left(1+\alpha\right)}{\ln \log_2 n}\right) \\
  &\geq  \frac{\ln \ln n}{\ln d} \cdot \left( 1+ o\left( 1\right)\right)
\end{align}

Then, 
\begin{align}
p_{swt} &\leq n \cdot 2^{{-d}^{\log_d\log_2 n + \log_d\left(1+\alpha\right)}} \\
		&= n \cdot 2^{-{d}^{\log_d\log_2 n}\cdot d^{\log_d \cdot\left(1+\alpha\right)}} \\
		&= n \cdot \left( 2^{-\log_2 n \cdot \left(1+ \alpha \right)} \right) \\
		&= n \cdot n^{-\left(1+\alpha\right)} = n^{-\alpha}
\end{align}

@@

A $d$-ary asymmetric witness tree of order $L$ has the structure of the Fibonacci tree $T_d(d \cdot L+1)$ and by Equation \ref{eqn:goldenFib} has $F_d(d\cdot L + 1) \geq \Phi_d^{d\cdot L-1}$ leaves.

@@

The above results imply the same probability for the activation of an asymmetric witness tree as we derived in Section \ref{sec:analysis:probabilitySymWT} for the activation of a symmetric witness tree, that is
\begin{align}
p_{awt} &\leq n \cdot 2^{-l}
\end{align}
However, the number of leaves is larger, since 
\begin{align}
l \geq \Phi_d^{d\cdot L -1}
\end{align}
holds\footnote{see Section \ref{sec:analysis:definitionAsymWT} for details}.

For any constant $\alpha > 0$, let 
\begin{align}
L &\geq \left\lceil{\frac{\ln\log_2 n + \ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d}}\right\rceil+\frac{1}{d}
\end{align}
\todo{the paper uses $+1$, instead of $+1/d$, but I can't make workout the below result then} and note that 
\begin{align}
L &\geq \frac{\ln\log_2 n}{d\cdot \ln \Phi_d} + \frac{\ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d} + \frac{1}{d}\\
  &\geq \frac{\ln\ln n}{d\cdot \ln \Phi_d} + O\left(1\right)
\end{align}

Then, 
\begin{align}
p_{awt} &\leq n \cdot 2^{-\Phi_d^{d\cdot L -1}} \\
        &= n \cdot 2^{-\Phi_d^{d\cdot \left(\left\lceil{\frac{\ln\log_2 n + \ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d}}\right\rceil+\frac{1}{d}\right) -1}} \\
        &\leq n \cdot 2^{-\Phi_d^{d\cdot \left({\frac{\ln\log_2 n + \ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d}}+\frac{1}{d}\right) -1}} \\
        &= n \cdot 2^{-\Phi_d^{{\frac{\ln\log_2 n + \ln\left(1+\alpha\right)}{d\cdot \ln \Phi_d}}}} \\
        &= n \cdot 2^{-\Phi_d^{\log_{\Phi_d}\log_2 n + \log_{\Phi_d}\left(1+\alpha\right)}} \\
         &= n \cdot 2^{-\Phi_d^{\log_{\Phi_d}\log_2 n}\cdot \Phi_d^{ \log_{\Phi_d}\left(1+\alpha\right)}} \\
         &= n \cdot 2^{-\log_2 n \cdot\left(1+\alpha\right)} \\
         &= n \cdot n ^{-(1+\alpha)} = n^{-\alpha}
\end{align}
